Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2020-04-30 paper.tex
R3: Typos, explain difference in scale in fig5+6, need to reply to him to motivate reason for not using real objects and why the largest number of guesses are placed in the centre intervals

Assuming these differences are normally distributed, we fit a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
We then used each CDF's parameters to determine a frequency cut-off threshold, where the participant could not longer reliably tell tones apart, which is set to contain 75\% of each participant's correct guesses.
The median of these threshold values can then be used to estimate the frequency difference at which the entire participant population can no longer tell the difference between two tones. 
It can also be used to improve the interface's frequency profile and performance. 
\cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value, which was found to be approximately 0.4 semitones for each group. 
\cref{fig:pitch-thresholds-hist} contains histograms of the cut-off frequency thresholds for each setting, which show that the settings can be grouped together.

@@

A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 threshold, was used to investigate the setting relationships more closely. 
This analysis reveals that there is a significant difference between the errors generated by the \textit{lo} and \textit{med} settings, as well as the \textit{lo} and \textit{hi} settings, for Group~\textit{G1} ($p_{lo-med} = 0.003,~p_{lo-hi} < 0.001$), showing that the \textit{lo} setting clearly produces the highest error, while it is not clear which one of the \textit{med} and \textit{hi} settings is better for Group~\textit{G1}. 
Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting. 
Furthermore, the significant variance in the error results for group \textit{G2} could possibly be because of the higher mean age compared to group \textit{G1} and their general inexperience with mobile phones.
However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).
The similarity between the differences is further highlighted with non-significant results from the two-sided Kolmogorov-Smirnov test ($p > 0.05$ for both groups and all three test conditions).\todo{include these p-values in the table?}
This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
Therefore, groups from a different population can reasonably be expected to produce similar errors under similar experimental conditions. 
We also note that there is a significant negative error bias in the elevation data for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
Since this bias seems to be constant, it could be easily addressed in a future version of the audio interface by adjusting its frequency parameters to shift the bias upwards by a constant offset. 
Finally, we can conclude that the \textit{hi} setting, which generates the significantly smallest elevation error, is the best audio pitch level to guide a user in a pointing task, and that the pan error is completely independent of such setting choice.

@@

For Group~\textit{G1}, a Fitts relationship can be observed and the logarithmic line of best fit closely approximates the median values of the binned data for all three settings. 
This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.76,~p_{lo} = 0.045;~r_{med} = 0.96,~p_{med}<0.001;~r_{hi} = 0.86,~p_{hi} = 0.013$).
Regarding Group~\textit{G2}¸ we observe larger spreads for each binned data plot, indicating less consistency in the time-to-target results for participants with severe sight impairments.
This could be due to each participant's result being taken as a single datum and to the smaller population size in Group~\textit{G2}.
Nevertheless, the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88,~p_{med} = 0.008;~r_{hi} = 0.84,~p_{hi} = 0.017$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.08,~p_{lo} = 0.85$).

>>>>

Assuming these differences are normally distributed, we fit a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
We then used each CDF's parameters to determine a frequency cut-off threshold, where the participant could not longer reliably tell tones apart, which is set to contain 75\% of each participant's correct guesses.
The median of these threshold values can then be used to estimate the frequency difference at which the entire participant population can no longer tell the difference between two tones. 
It can also be used to improve the interface's frequency profile and performance. 
\cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value, which was found to be approximately 0.4 semitones for each group. 
\cref{fig:pitch-thresholds-hist} contains histograms of the cut-off frequency thresholds for each setting, which show that the settings can be grouped together.
Note that the cut-off thresholds in \cref{fig:pitch-thresholds-hist} are transformed from the logarithmic semitone scale in \cref{fig:pitch-thresholds} to a linear Hertz-based scale for visualisation purposes to make the separation between the settings more clearly visible.

@@

A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 threshold, was used to investigate the setting relationships more closely. 
This analysis reveals that there is a significant difference between the errors generated by the \textit{lo} and \textit{med} settings, as well as the \textit{lo} and \textit{hi} settings, for Group~\textit{G1} ($p_{lo-med} = 0.003,~p_{lo-hi} < 0.001$), showing that the \textit{lo} setting clearly produces the highest error, while it is not clear which one of the \textit{med} and \textit{hi} settings is better for Group~\textit{G1}. 
Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting. 
Furthermore, the significant variance in the error results for Group \textit{G2} could possibly be because of the higher mean age compared to Group \textit{G1} and their general inexperience with mobile phones.
However, comparing the distributions for each setting between the two groups with the Kruskal-Wallis test for non-parametric data, we see that the differences between the distributions for all three settings are not significantly different, for both groups and both pan and elevation (the $p$-values are summarised in \cref{tab:inter-group-results}).
The similarity between the differences is further highlighted with non-significant results from the two-sided Kolmogorov-Smirnov test ($p > 0.05$ for both groups and all three test conditions).\todo{include these p-values in the table?}
This result confirms that the performance of the blindfolded participants and those with severe sight impairments are statistically similar despite the seemingly clear differences in error performance.
Therefore, groups from a different population can reasonably be expected to produce similar errors under similar experimental conditions. 
We also note that there is a significant negative error bias in the elevation data for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
Since this bias seems to be constant, it could be easily addressed in a future version of the audio interface by adjusting its frequency parameters to shift the bias upwards by a constant offset. 
Finally, we can conclude that the \textit{hi} setting, which generates the significantly smallest elevation error, is the best audio pitch level to guide a user in a pointing task, and that the pan error is completely independent of such setting choice.

@@

For Group~\textit{G1}, a Fitts relationship can be observed and the logarithmic line of best fit closely approximates the median values of the binned data for all three settings. 
This is confirmed by strong Pearson correlation scores for each setting ($r_{lo} = 0.76,~p_{lo} = 0.045;~r_{med} = 0.96,~p_{med}<0.001;~r_{hi} = 0.86,~p_{hi} = 0.013$).
Regarding Group~\textit{G2}¸ we observe larger spreads for each binned data interval, indicating less consistency in the time-to-target results for participants with severe sight impairments.
This could be due to each participant's result being taken as a single datum and to the smaller population size in Group~\textit{G2}, as well as the mean age and general level expertise with mobile devices of this particular group.
Nevertheless, the \textit{med} and \textit{hi} settings exhibit strong Pearson correlation scores ($r_{med} = 0.88,~p_{med} = 0.008;~r_{hi} = 0.84,~p_{hi} = 0.017$), while the results for the \textit{lo} setting does not produce a statistically significant correlation ($r_{lo} = 0.08,~p_{lo} = 0.85$).
